---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r data, include = FALSE}
library(tidyverse)
# reading in data
```

# group18package

<!-- badges: start -->
[![codecov](https://github.com/DSCI-310/dsci-310-group-18-pkg/actions/workflows/test-coverage.yaml/badge.svg)
<!-- badges: end -->

The goal of dsci310.visualizations.pkg is to generate images for a $kNN$ classification model that predicts patient heart disease severity using open source patient data from [Cleveland,Switzerland, VA Long Beach, & Hungary](https://archive.ics.uci.edu/ml/datasets/Heart+Disease). It provides convenience functions that generate nicely formatted visualizations with this classification model in mind. 

This package is built to aid in visualization generation from the start of a $kNN$ analysis to the end as it. This package makes generating EDA visualizations, model building visualizations, and result visualizations easy!

This package is a combination of `cowplot` & `ggplot2`. It also uses functions from the `tidymodels`& `tidyverse` packages. `dsci310.visualization.pkg` is made to be a convenient combination of all the above packages that has pre-formatted visualizations for a heart disease severity classification. 

## Installation

You can install the development version of dsci310.visualizations.pkg from [GitHub](https://github.com/) with:

```{r loading, results = 'hide', message = FALSE}
# install.packages("devtools")
devtools::install_github("DSCI-310/dsci-310-group-18-pkg")
```

# Package Functions:

- [`grid_boxplot()`](#grid_boxplot())
- [`majority_classifier_vis_function()`](#majority_classifier_vis_function())
- [`knn_visualization()`](#knn_visualizations)

## Usage:

*All examples were generated using this [data](https://raw.githubusercontent.com/DSCI-310/dsci-310-group-18/main/data/processed/heart_data.csv).

In order to use any of the functions the library must be called:
```{r library, message = FALSE, results = 'hide'}
library(group18package)
```

### grid_boxplot()

The function `grid_boxplot()` takes in a R data frame with factor `diagnosis_f` & a specified numeric type variable. `grid_boxplot()` then produces a boxplot that shows the range of the numeric variable each level of heart severity lies in.

In this example we are using [heart_data](https://raw.githubusercontent.com/DSCI-310/dsci-310-group-18/main/data/processed/heart_data.csv), the factor variable is `diagnosis_f`, the numeric variable is `age`.

```{r grid_boxplot}
boxplot <- grid_boxplot(data = training_split_new, xAxis = as.factor(training_split_new$diagnosis_f), yAxis = age, yLabel = "Age (Years)", titleLabel = "Severity of heart disease \n compared to age of patient")
boxplot
```

Notice how `grid_boxplot` displays differences of the factor variable over the numeric variable. This type of visualization can be very helpful for early data visualization and question development!

### majority_classifier_vis_function()

`majority_classifier_vis_function()` produces a graph that displays the percent of rows belonging to each category in a factor variable of interest. 

This function produces a bar plot that has the degree of heart disease severity on the x-axis and the percent of rows in the data on the y-axis. 

This function is a convenient shortcut when determining if there is a categorical imbalance in the data you are using to build your model. 

```{r majority_classifier_vis_function}
maj_vis <- majority_classifier_vis_function(data = majority_classifier, 
                                 hGraph = 5, 
                                 wGraph = 7, 
                                 textSize = 12, 
                                 colWidth = 0.5, 
                                 xLabel = "Heart disease degree of severity", 
                                 yLabel = "Percent of outcomes \n in training dataset", 
                                 titleLabel = "Label proportions of \n classifier in dataset")
maj_vis
```

### knn_visualization()

`knn_visualization()` produces a visualization of the number of neighbors against accuracy estimate. This type of visualization is very useful when trying to determine the number of neighbors to use in a kNN model. 

`knn_visualization` generates a visualization that provides more context to the accuracy values than simply looking at the numbers. It ensures the choice for the number of neighbors is informed in a simple and easily executable way. 

The function `knn_visualization()`
```{r knn_visualization}
knn_visualization(data = heart_data_accuracies)
```
