---
title: "dsci-310-group-18-pkg-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dsci-310-group-18-pkg-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


This is the documentation of how to use the dsci18pkg package for useful functions that you may need for your data analysis on heart data.

# Package Functions:

- [`grid_boxplot()`](#grid_boxplot())
- [`majority_classifier_vis_function()`](#majority_classifier_vis_function())
- [`knn_visualization()`](#knn_visualizations)

## Usage:

\*All examples were generated using this
[data](https://raw.githubusercontent.com/Dokkaebi10/dsci-310-group-18/main/data/processed/heart_data.csv).

In order to use any of the functions the library must be called:

```{r setup}
library(group18package)
```

### grid_boxplot()

The function `grid_boxplot()` takes in a R data frame with factor
`diagnosis_f` & a specified numeric type variable. `grid_boxplot()` then
produces a boxplot that shows the range of the numeric variable each
level of heart severity lies in.

In this example we are using
[heart_data](https://raw.githubusercontent.com/Dokkaebi10/dsci-310-group-18/main/data/processed/heart_data.csv),
the factor variable is `diagnosis_f`, the numeric variable is `age`.

``` {r grid_boxplot}
age <- 0:10
max_heart_rate <- 0:10
diagnosis_f <- factor(c(1,2,3,4,0,1,2,3,4,0,1))
heart_data <- data.frame(max_heart_rate, age, diagnosis_f)
boxplot <- grid_boxplot(heart_data, diagnosis_f, age, "Age (Years)", "Severity of heart disease \n compared to age of patient")
boxplot
```

Notice how `grid_boxplot` displays differences of the factor variable
over the numeric variable. This type of visualization can be very
helpful for early data visualization and question development!

### majority_classifier_vis_function()

`majority_classifier_vis_function()` produces a graph that displays the
percent of rows belonging to each category in a factor variable of
interest.

This function produces a bar plot that has the degree of heart disease
severity on the x-axis and the percent of rows in the data on the
y-axis.

This function is a convenient shortcut when determining if there is a
categorical imbalance in the data you are using to build your model.

``` {r majority_classifier_vis_function}
maj_vis <- majority_classifier_vis_function(data = majority_classifier)
maj_vis
```

### knn_visualization()

`knn_visualization()` produces a visualization of the number of
neighbors against accuracy estimate. This type of visualization is very
useful when trying to determine the number of neighbors to use in a kNN
model.

`knn_visualization` generates a visualization that provides more context
to the accuracy values than simply looking at the numbers. It ensures
the choice for the number of neighbors is informed in a simple and
easily executable way.

The function `knn_visualization()`

``` {r knn_visualization}
knn_visualization(heart_data_accuracies)
```
